Draft genomes of the three northern hemisphere blue mussel lineages: North and South European \emph{Mytilus edulis} and Mediterranean \emph{Mytilus galloprovincialis}.

### 2022-06-22 manuscript/ms_genomes.tex
species tree

>>>>

The species tree (\cref{fig:tree}) shows that the assemblies and the published genomes and transcriptomes are clustering as expected.
\texttt{Orthofinder} \comment{provides}{provide the orthogroups somewhere} a resource of single-copy orthogroups across a large part the \textit{Mytilus} species complex.

\begin{figure}[h]
	\includegraphics[width=\linewidth]{figures/Fig3_tree.pdf}
	\caption{Species tree using 1300 orthogroups with minimum of 81.8\% of species having single-copy genes in any orthogroup.
	Color coding -- dark blue: \textit{M. edulis} Europe, light blue: \textit{M. edulis} America,
	red: \textit{M. galloprovincialis} Mediterranean Sea, yellow: \textit{M. galloprovincialis} Atlantic,
	green: \textit{M. trossulus}, pink: \textit{M. coruscus}, gray: \textit{M. californianus}.
	}
	\label{fig:tree}
\end{figure}
